Networks Matter in International Relations:\\A Latent Network Approach to Analysis

### 2017-10-22 paper/4_app.tex
marg eff fix

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our re-estimation using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one. Our re-estimation using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework. Finally, our modeling approach outperforms the original model by better, and more accurately, predicting MIDs out-of-sample (Figure~\ref{fig:reitaucpr}).

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{reiter_stam_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{reiter_stam_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

@@

We utilized the original and the AME results from Gibler's model 6 in Table 6 to calculate the expected values for one scenario. We focused on the variables measuring rivalry.  We used mean or modal values for all independent variables, except we changed the rivalry variable to indicate that there was a rivalry when the actual data suggest there is none.  The expected values of this scenario are essentially a first difference plot comparing results with the model when estimated in two different ways: Gibler's GLM estimation and our AME approach.  As this Figure~\ref{fig:gibmargeff} illustrates, the AME results differ from the GLM in two distinct ways. First, the expected value of the dependent variable---the probability of the onset of a militarized interstate dispute, is considerably higher when taking interdependencies into account with the AME model.  These are rare events, so the probabilities are low, but the difference is a factor of $3x$. Thus, you get quite substantially different expected values from these two models.  Second, the GLM model has a standard errors which underestimate the true variability, in part because some of them are assumed to be zero.  This shows up in the narrow density of predicted outcomes for the GLM model, compared to the density seen with the AME. The latter reflects a wider range of potential outcomes, reflecting the incorporation of uncertainty in the AME model.

>>>>

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our re-estimation using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one. Our re-estimation using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework.

@@

We utilized the original and the AME results from Gibler's model 6 in Table 6 to calculate the expected values for one scenario. We focused on the variables measuring rivalry.  We used mean or modal values for all independent variables, except we changed the rivalry variable to indicate that there was a rivalry when the actual data suggest there is none.  The expected values of this scenario are essentially a first difference plot comparing results with the model when estimated in two different ways: Gibler's GLM estimation and our AME approach.  As this Figure~\ref{fig:gibmargeff} illustrates, the AME results differ notable. First, the expected value of the dependent variable---the probability of the onset of a militarized interstate dispute, is considerably lower when taking interdependencies into account with the AME model.  These are rare events, so the probabilities are low, but the difference is a factor of almost 2. Thus, you get quite substantially different expected values from these two models.

### 2017-10-22 paper/6_appendix.tex
stargazer tables
more clean up we are at 99%
marg eff fix

\subsection*{Performance Analysis}

@@

@@

\subsubsection*{McDonald (2004)}

@@

\subsubsection*{Reiter \& Stam (2003)}

@@

\subsubsection*{Rose (2004)}

% \begin{figure}
% 	\centering   
% 	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{mcdonald_roc_outSample.pdf}}
% 	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{mcdonald_pr_outSample.pdf}}
% 	\caption{Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
% \end{figure}
% \FloatBarrier

\subsubsection*{Weeks (2012)}

\begin{figure}
	\centering   
	\subfigure[AUC]{\label{fig:weeksroc}\includegraphics[width=.45\textwidth]{weeks_roc_outSample.pdf}}
	\subfigure[Precision and Recall]{\label{fig:weekspr}\includegraphics[width=.45\textwidth]{weeks_pr_outSample.pdf}}
	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves.}
\end{figure}
\FloatBarrier

>>>>

\subsection*{Additional Replication Information}

@@

Coefficient plot and performance comparison.

\input{gibler_coeftable}
\FloatBarrier

@@

\clearpage
\subsubsection*{McDonald (2004)}

Coefficient plot and performance comparison.

\input{mcdonald_coeftable}
\FloatBarrier

@@

\clearpage
\subsubsection*{Reiter \& Stam (2003)}

Coefficient plot and performance comparison.

\input{reiter_stam_coeftable}
\FloatBarrier

@@

\clearpage
\subsubsection*{Rose (2004)}

Coefficient plot and performance comparison.

\input{rose_coeftable}
\FloatBarrier

% \begin{figure}
% 	\centering   
% 	\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=.45\textwidth]{mcdonald_roc_outSample.pdf}}
% 	\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=.45\textwidth]{mcdonald_pr_outSample.pdf}}
% 	\caption{Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
% \end{figure}
\FloatBarrier

\clearpage
\subsubsection*{Weeks (2012)}

Coefficient plot and performance comparison.

\input{weeks_coeftable}
\FloatBarrier

% already show roc-pr in main text
% \begin{figure}
% 	\centering   
% 	\subfigure[AUC]{\label{fig:weeksroc}\includegraphics[width=.45\textwidth]{weeks_roc_outSample.pdf}}
% 	\subfigure[Precision and Recall]{\label{fig:weekspr}\includegraphics[width=.45\textwidth]{weeks_pr_outSample.pdf}}
% 	\caption{Assessments of out-of-sample predictive performance for Weeks (2012) using ROC curves and PR curves.}
% \end{figure}
% \FloatBarrier
